Enhancement of SDR in Thessaloniki

### 2024-03-02 GHI_enh_04_investigate.tex
Commit 2024-03-02 15:11

Units for GLB\_diff.max : Watt/m\^{}2lmD: 1.566022 +/- 0.1083205

@@

Units for GLB\_diff.mean : Watt/m\^{}2lmD: 0.9508227 +/- 0.1552488

@@

Units for GLB\_diff.median : Watt/m\^{}2lmD: 1.087008 +/- 0.1678713

@@

Units for GLB\_diff.N : lmD: -0.01234536 +/- 0.1388793

@@

Units for GLB\_diff.sum : kJ/m\^{}2lmD: 33.66074 +/- 5.692733

@@

Units for GLB\_ench.max : Watt/m\^{}2lmD: 0.003266094 +/- 0.0002706818

@@

Units for GLB\_ench.mean : Watt/m\^{}2lmD: 0.001714795 +/- 0.0002777698

@@

Units for GLB\_ench.median : Watt/m\^{}2lmD: 0.001677055 +/- 0.00031363

@@

Units for GLB\_ench.N : lmD: -0.01234536 +/- 0.1388793

@@

Units for GLB\_ench.sum : Watt/m\^{}2lmD: 0.9770213 +/- 0.1439346

@@

Units for GLB\_diff.max : Watt/m\^{}2lmD: 0.8175146 +/- 0.1034317

@@

Units for GLB\_diff.mean : Watt/m\^{}2lmD: 0.2160878 +/- 0.03807227

@@

Units for GLB\_diff.median : Watt/m\^{}2lmD: 0.1909484 +/- 0.03787569

@@

Units for GLB\_diff.N : lmD: 0.4856759 +/- 0.04638817

@@

Units for GLB\_diff.sum : kJ/m\^{}2lmD: 1467.856 +/- 152.6556

@@

Units for GLB\_ench.max : Watt/m\^{}2lmD: 0.001335923 +/- 0.0001367163

@@

Units for GLB\_ench.mean : Watt/m\^{}2lmD: 0.000422753 +/- 5.903214e-05

@@

Units for GLB\_ench.median : Watt/m\^{}2lmD: 0.000372438 +/- 6.132797e-05

@@

Units for GLB\_ench.N : lmD: 0.4856759 +/- 0.04638817

@@

Units for GLB\_ench.sum : Watt/m\^{}2lmD: 0.03656094 +/- 0.003621568

@@

Units for GLB\_diff.max : Watt/m\^{}2lmD: 0.1872432 +/- 0.2494753

@@

Units for GLB\_diff.mean : Watt/m\^{}2lmD: 0.0498083 +/- 0.192504

@@

Units for GLB\_diff.median : Watt/m\^{}2lmD: 0.0912832 +/- 0.1914519

@@

Units for GLB\_diff.N : lmD: 0.03034705 +/- 0.02124537

@@

Units for GLB\_diff.sum : kJ/m\^{}2lmD: 0.3683616 +/- 0.2534977

@@

Units for GLB\_ench.max : Watt/m\^{}2lmD: 0.0005085756 +/- 0.0002811408

@@

Units for GLB\_ench.mean : Watt/m\^{}2lmD: 0.0003565528 +/- 0.0002141263

@@

Units for GLB\_ench.median : Watt/m\^{}2lmD: 0.000398809 +/- 0.0002210804

@@

Units for GLB\_ench.N : lmD: 0.03034705 +/- 0.02124537

@@

Units for GLB\_ench.sum : Watt/m\^{}2lmD: 0.008776506 +/- 0.00550671

@@

\begin{verbatim}
2024-03-02 09:46:24.0 athan@tyler GHI_enh_04_investigate.R 0.976988 mins
\end{verbatim}

>>>>

Units for GLB\_diff.max : Watt/m\^{}2

lmD: 1.566022 +/- 0.1083205

@@

Units for GLB\_diff.mean : Watt/m\^{}2

lmD: 0.9508227 +/- 0.1552488

@@

Units for GLB\_diff.median : Watt/m\^{}2

lmD: 1.087008 +/- 0.1678713

@@

Units for GLB\_diff.N :

lmD: -0.01234536 +/- 0.1388793

@@

Units for GLB\_diff.sum : kJ/m\^{}2

lmD: 33.66074 +/- 5.692733

@@

Units for GLB\_ench.max : Watt/m\^{}2

lmD: 0.003266094 +/- 0.0002706818

@@

Units for GLB\_ench.mean : Watt/m\^{}2

lmD: 0.001714795 +/- 0.0002777698

@@

Units for GLB\_ench.median : Watt/m\^{}2

lmD: 0.001677055 +/- 0.00031363

@@

Units for GLB\_ench.N :

lmD: -0.01234536 +/- 0.1388793

@@

Units for GLB\_ench.sum : Watt/m\^{}2

lmD: 0.9770213 +/- 0.1439346

@@

Units for GLB\_diff.max : Watt/m\^{}2

lmD: 0.8175146 +/- 0.1034317

@@

Units for GLB\_diff.mean : Watt/m\^{}2

lmD: 0.2160878 +/- 0.03807227

@@

Units for GLB\_diff.median : Watt/m\^{}2

lmD: 0.1909484 +/- 0.03787569

@@

Units for GLB\_diff.N :

lmD: 0.4856759 +/- 0.04638817

@@

Units for GLB\_diff.sum : kJ/m\^{}2

lmD: 1467.856 +/- 152.6556

@@

Units for GLB\_ench.max : Watt/m\^{}2

lmD: 0.001335923 +/- 0.0001367163

@@

Units for GLB\_ench.mean : Watt/m\^{}2

lmD: 0.000422753 +/- 5.903214e-05

@@

Units for GLB\_ench.median : Watt/m\^{}2

lmD: 0.000372438 +/- 6.132797e-05

@@

Units for GLB\_ench.N :

lmD: 0.4856759 +/- 0.04638817

@@

Units for GLB\_ench.sum : Watt/m\^{}2

lmD: 0.03656094 +/- 0.003621568

@@

Units for GLB\_diff.max : Watt/m\^{}2

lmD: 0.1872432 +/- 0.2494753

@@

Units for GLB\_diff.mean : Watt/m\^{}2

lmD: 0.0498083 +/- 0.192504

@@

Units for GLB\_diff.median : Watt/m\^{}2

lmD: 0.0912832 +/- 0.1914519

@@

Units for GLB\_diff.N :

lmD: 0.03034705 +/- 0.02124537

@@

Units for GLB\_diff.sum : kJ/m\^{}2

lmD: 0.3683616 +/- 0.2534977

@@

Units for GLB\_ench.max : Watt/m\^{}2

lmD: 0.0005085756 +/- 0.0002811408

@@

Units for GLB\_ench.mean : Watt/m\^{}2

lmD: 0.0003565528 +/- 0.0002141263

@@

Units for GLB\_ench.median : Watt/m\^{}2

lmD: 0.000398809 +/- 0.0002210804

@@

Units for GLB\_ench.N :

lmD: 0.03034705 +/- 0.02124537

@@

Units for GLB\_ench.sum : Watt/m\^{}2

lmD: 0.008776506 +/- 0.00550671

@@

\begin{verbatim}
2024-03-02 12:29:58.0 athan@tyler GHI_enh_04_investigate.R 1.354976 mins
\end{verbatim}
